---
title: "Shepherd SR model"
author: "I Paya"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Formula taken from FLR FLCore Stock-Recruitment models.  

Shepherd stock-recruitment model fit: 
$$R = \frac{a S}{1+(\frac{S}{b})^c}$$ a represents density-independent survival (similar to a in the Ricker stock-recruit model), b the stock size above which density-dependent processes predominate over density-independent ones (also referred to as the threshold stock size), and c the degree of compensation.

and with Shepherd stock-recruitment model:
$$R_j = \frac{a SBT_{j-1}}{1+(\frac{SBT_{j-1}}{b})^c}$$ 

Shepherd stock-recruitment model parameterized for steepness and virgin biomass.
$$b = SB0 (\frac{0.2-h}{h (0.2)^c - 0.2})^ (\frac{-1.0}{c})$$

$$a = \frac{1.0+(\frac{SB0}{b})^c}{SBPR}$$
Example 1
```{r}
#Example
SB0=100
SBPR=12
h=0.7
c=1.8
b=SB0*((0.2-h/(h*0.2)^c-0.2))*(-1/c)
a=(1 + (SB0/b)^c)/SBPR
SBT=seq(100,10000,10)
R=SBT*0
for(i in 2:length(SBT)){
   R[i]=(a*SBT[i-1])/(1+(SBT[i-1]/b)^c)  
   }
plot(SBT[1:(length(SBT)-1)],R[2:(length(SBT))],"l")
#a
#b
```
Example 2
```{r}
#Example 2
SB0=100
SBPR=12
h=0.7
c=0.8
b=SB0*((0.2-h/(h*0.2)^c-0.2))*(-1/c)
a=(1 + (SB0/b)^c)/SBPR
SBT=seq(100,10000,10)
R=SBT*0
for(i in 2:length(SBT)){
   R[i]=(a*SBT[i-1])/(1+(SBT[i-1]/b)^c)  
   }
plot(SBT[1:(length(SBT)-1)],R[2:(length(SBT))],"l")
#a
#b
```